\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,top=1.25cm,bottom=1.25cm,left=1.35cm,right=1.35cm]{geometry}

% XeLaTeX / LuaLaTeX font setup
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{microtype}

\setmainfont{TeX Gyre Heros}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{needspace}
\usepackage{ragged2e}

\definecolor{accent}{HTML}{0F4C81}
\definecolor{accentdark}{HTML}{0B355A}
\definecolor{textmain}{HTML}{111827}
\definecolor{textmuted}{HTML}{4B5563}
\definecolor{linegray}{HTML}{D1D5DB}
\definecolor{softgray}{HTML}{F3F4F6}

\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2.5pt}
\renewcommand{\arraystretch}{1.18}

\setlist[itemize]{leftmargin=1.15em,topsep=2pt,itemsep=1.5pt,parsep=0pt,partopsep=0pt}

\titleformat{\section}
  {\needspace{6\baselineskip}\large\bfseries\color{accentdark}}
  {}{0pt}{}[\vspace{-2pt}{\color{accent}\titlerule[0.8pt]}]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\newcommand{\cvtag}[1]{%
  \begingroup
  \setlength{\fboxsep}{3pt}%
  \colorbox{softgray}{\strut\small #1}%
  \endgroup
}

\newcommand{\role}[4]{%
  \Needspace{5\baselineskip}%
  \vspace{3pt}%
  {\bfseries\color{textmain}#1}\hfill {\small\color{textmuted}#2}\\[-1pt]
  {\itshape\color{accentdark}#3}\hfill {\small\color{textmuted}#4}\\[-4pt]
  {\color{linegray}\rule{\textwidth}{0.35pt}}\vspace{-3pt}
}

\newcommand{\compactrole}[4]{%
  \Needspace{3\baselineskip}%
  {\bfseries #1}\hfill {\small\color{textmuted}#2}\\[-1pt]
  {\itshape\color{accentdark}#3}\hfill {\small\color{textmuted}#4}\vspace{2pt}
}

\newcommand{\metric}[2]{%
  \begin{minipage}[t]{0.31\textwidth}
    {\Large\bfseries\color{accentdark}\mbox{#1}}\\[-2pt]
    {\small\color{textmuted}#2}
  \end{minipage}%
}

\begin{document}

% ===== Header =====
\begin{minipage}[t]{0.64\textwidth}
  {\Huge\bfseries\color{textmain} Łukasz Piotr Łuczak}\\[2pt]
  {\Large\color{accentdark} Solution Architect / Principal Engineer}\\[4pt]
  {\color{textmuted}Web Platforms \textbullet{} Frontend Architecture \textbullet{} Integrations \textbullet{} Technical Leadership}
\end{minipage}
\hfill
\begin{minipage}[t]{0.34\textwidth}
  \raggedleft\small
  Łódź, Poland \textbullet{} Remote / Hybrid\\
  Full-time employment or long-term contract\\[2pt]
  \href{mailto:lukasz@luczak.tech}{lukasz@luczak.tech} \textbullet{} +48 535 015 006\\
  \href{https://github.com/lukaszpiotrluczak}{github.com/lukaszpiotrluczak}\\
  \href{https://www.linkedin.com/in/lukaszpiotrluczak/}{linkedin.com/in/lukaszpiotrluczak}
\end{minipage}

\vspace{7pt}
{\color{accent}\rule{\textwidth}{1.2pt}}
\vspace{4pt}

\begin{tabularx}{\textwidth}{@{}X X X@{}}
\metric{18+ years}{commercial software engineering} &
\metric{20 engineers}{largest led / supported team} &
\metric{Architecture}{hands-on delivery and consulting}
\end{tabularx}

\section{Professional Summary}

Solution Architect / Principal Engineer with 18 years of commercial software engineering experience, focused on web platforms, frontend architecture, integrations, analytical systems and complex business applications. Combines hands-on engineering with architecture ownership, technical leadership, mentoring, code review, CI/CD, quality standards, estimation and client-facing consulting. Experienced in leading teams of up to 20 engineers, supporting 12--15 developers directly, and quickly entering unknown or troubled projects to unblock design, performance and implementation issues.

\section{Selected Impact}

\begin{itemize}
  \item Led and mentored frontend/software engineering teams of up to 20 people, directly supporting 12--15 engineers through architecture guidance, code review and delivery problem-solving.
  \item Designed and implemented ``Expressions'', a browser-based business expression language with parser, editor, runtime, validation, API, BDD tests and multi-format build system for SAP ecosystem products used by Fortune 500-class enterprise customers.
  \item Designed and optimized a React/.NET analytical web application supporting financial statement audit workflows at PwC Advisory.
  \item Led architecture and development of a car-sharing and scooter-sharing platform as CTO / Chief Architect, enabling real business operations.
  \item Designed a microservices PoC and contributed to deployment of a scalable live-chat communication channel for high-traffic e-commerce.
  \item Supported discovery, sales and client-facing architecture work, including solution design, estimates, technical offers and delivery risk assessment.
\end{itemize}

\section{Core Competencies}

\cvtag{Solution Architecture}\hspace{3pt}
\cvtag{Principal Engineering}\hspace{3pt}
\cvtag{Frontend Architecture}\hspace{3pt}
\cvtag{Web Platforms}\hspace{3pt}
\cvtag{Technical Leadership}\hspace{3pt}
\cvtag{Architecture Reviews}\hspace{3pt}
\cvtag{API Design}\hspace{3pt}
\cvtag{Integration Architecture}\hspace{3pt}
\cvtag{Microservices}\hspace{3pt}
\cvtag{Modular Monoliths}\hspace{3pt}
\cvtag{Event-Driven Systems}\hspace{3pt}
\cvtag{Analytical Dashboards}\hspace{3pt}
\cvtag{Workflow Systems}\hspace{3pt}
\cvtag{Legacy Modernization}\hspace{3pt}
\cvtag{Performance Optimization}\hspace{3pt}
\cvtag{CI/CD}\hspace{3pt}
\cvtag{Testing Strategy}\hspace{3pt}
\cvtag{Code Review}\hspace{3pt}
\cvtag{Quality Gates}\hspace{3pt}
\cvtag{Discovery Workshops}\hspace{3pt}
\cvtag{Estimation}\hspace{3pt}
\cvtag{Mentoring}

\section{Technical Stack}

\begin{tabularx}{\textwidth}{@{}>{\bfseries\color{accentdark}}p{3.4cm}X@{}}
Frontend & TypeScript, JavaScript, React, Angular, Nx, Microfrontends, SSR/SSG, Playwright, Jest/Vitest, Web Components, Canvas \\
Backend \& Data & Node.js, PHP, Python, SQL, PostgreSQL, MySQL/MariaDB, REST, GraphQL, Message Queues \\
Architecture & DDD, Clean Architecture, Hexagonal Architecture, Event Storming, ADRs, API Design, Integration Architecture, Security-Aware Architecture \\
DevOps \& Infra & Docker, Podman, Linux, Nginx, GitHub Actions, CI/CD, Proxmox, OpenTelemetry, Prometheus/Grafana \\
\end{tabularx}

\section{Professional Experience}

\role{Independent Technology Consultant}{09.2023--present}{Luczak Consulting}{Łódź / Remote}
Provides selected architecture and implementation consulting services for web and business platforms. Currently available for full-time employment or long-term contract engagement.

\role{Frontend TechLead / Senior Software Engineer}{10.2021--08.2023, 06.2024--05.2025}{SoftwareHut}{Remote / Poland}
\begin{itemize}
  \item Led and mentored a team of 12--15 frontend engineers while participating in delivery projects as a senior hands-on engineer and architecture advisor.
  \item Designed frontend architectures, performed code reviews across own and external projects, and supported teams with expert-level frontend and web platform knowledge.
  \item Participated in discovery and sales meetings, prepared solution architectures, technical estimates and implementation offers.
  \item Frequently brought into unfamiliar or troubled projects to diagnose issues, unblock implementation problems and support delivery.
  \item Selected work included a healthcare services directory with appointment registration integrated with a government API, and a platform for modelling and designing autonomous warehouse systems.
\end{itemize}

\role{Trainer / Architecture Consultant}{11.2017--08.2023}{Symentis}{Poland}
\begin{itemize}
  \item Delivered around 20 B2B workshops and training programs, totaling approximately 160 hours for about 100 unique participants, from junior developers to architects.
  \item Responsible for needs analysis, training scope definition, content preparation and delivery.
  \item Provided architecture and engineering consulting beyond training engagements, supporting teams in software design, project practices and technical decision-making.
\end{itemize}

\role{Senior Software Developer / Principal Frontend Engineer}{04.2017--11.2021}{Vistex Poland-CEE}{Poland}
\begin{itemize}
  \item Designed and implemented ``Expressions'', a business expression language used across enterprise planning, pricing and modelling tools distributed within the SAP ecosystem.
  \item Started from Excel-like expressions and iteratively evolved the language into a richer system supporting loops, cursors over datasets, dataset pointers, pattern matching and advanced business rules.
  \item Owned syntax design, parser implementation, browser-based editor integration, validation, runtime, public API, test strategy and a complex multi-format build system producing AMD, UMD, RequireJS, ES6 and SystemJS packages.
  \item Provided informal frontend technical leadership for enterprise products used by global Fortune 500-class SAP customers.
\end{itemize}

\role{Architecture and Technology Consultant}{07.2019--12.2019}{PwC Advisory}{Poland}
\begin{itemize}
  \item Designed and optimized a React/.NET analytical web application supporting financial statement audit workflows.
  \item The system presented financial documents dynamically, enabled text selection and annotations, and visualized references and correlations between values across rows, pages and tables.
  \item Focused on solution architecture, frontend performance and usability of complex document-analysis workflows.
\end{itemize}

\role{CTO / Chief Architect / Lead Developer}{07.2014--06.2021}{Inn4Tech / Citicar}{Poland}
\begin{itemize}
  \item Led architecture and development of a car-sharing and scooter-sharing platform as CTO, architect and lead developer.
  \item Managed a 7-person team and was responsible for technology decisions, product architecture, implementation direction and delivery.
  \item Delivered a platform supporting real car-sharing business operations and the core software required to run the service.
\end{itemize}

\role{Senior Fullstack Developer}{03.2016--03.2017}{STX Next}{Poland}
\begin{itemize}
  \item Worked in a 20-person delivery environment on data-heavy web systems, including an analytical dashboard for quant developers and a migration of a pension fund management solution from Oracle Forms / legacy environment to a modern web application.
  \item Focused on full-stack implementation, data integration, performance and maintainability using Python and JavaScript.
\end{itemize}

\role{Senior Software Developer / Solution Architect}{10.2014--02.2016}{Focus Telecom Polska}{Poland}
\begin{itemize}
  \item Designed architecture and prepared a microservices PoC for a new customer communication channel.
  \item Contributed to implementation and deployment of a live-chat solution capable of handling traffic from a large e-commerce website and competing with dedicated live-chat platforms.
  \item Worked with PHP, Symfony, Propel, PostgreSQL and Node.js in a 16-person team.
\end{itemize}

\role{Senior Software Developer / Solution Architect}{09.2012--09.2014}{Ericpol}{Poland}
\begin{itemize}
  \item Designed and led frontend implementation for a web platform supporting application, assessment and processing workflows for cross-border funding programs.
  \item Led a 6-person implementation team and delivered a web panel with a dynamic reporting module allowing users to define reports at runtime.
  \item Worked with PHP, JavaScript and Java.
\end{itemize}

\role{Programmer \& Administrator / Developer}{07.2007--08.2014}{Lodz University of Technology}{Łódź, Poland}
\begin{itemize}
  \item Designed, developed and maintained university support systems.
  \item Developed the EECS Student Connectivity Module, a distributed system for secure student data exchange between universities with electronic document workflow support.
\end{itemize}

\section{Education, Research and Certifications}

\begin{itemize}
  \item \textbf{PhD Candidate, Information and Communications Technologies}, Lodz University of Technology, 2022--present. Research: models and algorithms for traffic management in multipath network transmission.
  \item \textbf{M.Sc., Electronics and Telecommunications}, Lodz University of Technology, 2004--2012. Specialty: Signal and Image Processing.
  \item \textbf{Researcher}, National Science Centre, Poland, 03.2023--01.2025. Project no. 2021/41/B/ST7/00108: Robust Control Solutions for Multi-Channel Networked Flows.
  \item \textbf{Internal Auditor of Information Security Management System}, PN-EN ISO/IEC 27001:2017, Dekra, 2020.
  \item \textbf{Internal Auditor of Integrated Management System}, ISO 9001:2015, ISO 14001:2015, ISO 45001:2018, Dekra, 2019.
\end{itemize}

\section{Publications, Teaching and Community}

\begin{itemize}
  \item Peer-reviewed publications on MPTCP congestion control, streaming QoS and multipath transmission, including Future Internet, FedCSIS, EuroSPI² and Annals of Computer Science and Information Systems.
  \item Lecturer at Uniwersytet Dolnośląski DSW, 10.2023--09.2025: Magento, Python and Cybersecurity.
  \item Speaker and workshop host at Polish IT conferences and meetups, including 4Developers, SegFault, Warsaw IT Days, meet.js and ByteBay.
  \item Program committee member for 4Developers tracks: JavaScript, Application Architectures, Frontend and Databases.
\end{itemize}

\section{Languages}

Polish -- native \textbullet{} English -- C1, professional working proficiency, technical documentation and academic writing

\end{document}
